---
title: "R Notebook"
output: html_notebook
---
## Goodreads Books Analysis 
## Exploratory Data Analysis (EDA)
## Haifaa Alzahrani
## 21/10/2020

Note: The used dataset is not reliable, it has duplication issues and needs to manually verified. However, the aim of this project is just to apply the skills rather than building reliable model. 

### Initialise libraries
```{r}
library(tidyverse)
```

```{r}
dataset <- read_csv("~/MISK_DSI/R/DS_Research_GoodreadsBooks/Data/full_books.csv")

# Overview
glimpse(dataset)

```

```{r}
# Remove X
dataset <- dataset %>%
  select(-X1)
```

Exploratory Data Analysis (EDA) and Visualization

```{r}
# Repeated books' titles
sum(duplicated(dataset$title)) # 775 repeated titles
```

```{r}
# Number of authors
dataset$authors %>% 
  unique() %>% length() # 4215
```

There are duplicated books due to adding different parts or edition as separated books.
```{r}
# To view the top 25 highest repeated books
dataset %>%
  group_by(title) %>%
  summarise(Number = n()) %>%
  arrange(-Number) %>%
  head(n=25) %>%  
  ggplot(aes(x=reorder(title, Number), y=Number)) +
  geom_col(alpha=0.7, fill = "red") +
  coord_flip() +
  labs(x="Title", y="Number of books")+
  ggtitle('Repeated books titles')
```
The most 10 popular authors according to rating count for their books
```{r}
dataset %>%
  group_by(authors) %>%
  summarise(rating_sum = sum(ratings_count)) %>%
  arrange(-rating_sum)  %>%
  top_n(10) %>%
  ggplot(aes(x = reorder(authors, rating_sum), y = rating_sum)) + 
  geom_col(alpha=0.7, fill = "blue") +
  labs(x = "Author", y = "Sum of Ratings") +
  ggtitle("Most Popular Authors")+
  coord_flip()
```
The books that got the highest 25 number ratings.
To learn the most popular books.
```{r}
dataset %>%
  group_by(title) %>%
  arrange(-ratings_count) %>%
  top_n(25)  %>%
  select(title, authors, ratings_count, average_rating)
  #ggplot(aes(x = reorder(title, ratings_count), y = ratings_count)) + 
  #geom_col(alpha=0.7) +
  #scale_fill_brewer(palette = "Set3") +
  #labs(x = "Book Title", y = "Number of Ratings") +
  #ggtitle("Most Popular Books")+
  #coord_flip()
```
The books that got the highest 25 count of reviews. 
To know which books motivate readers to discuss about them 
```{r}
dataset %>%
  group_by(title) %>%
  arrange(-text_reviews_count) %>%
  top_n(25)  %>%
  select(title, authors, text_reviews_count, average_rating)
```
Popular books that got the highest 25 ratings.
To know the most favorite books.
```{r}
dataset %>%
  group_by(title) %>%
  arrange(-average_rating) %>%
  top_n(25)  %>%
  select(title, authors, average_rating)
```
Top 25 years according to the number of the published books
```{r}
# Inaccurate results!
dataset %>%
  count(publication_date, name = "number of books", sort = TRUE) %>%
  top_n(25) 
```
Does the number of pages affect rating counts? 
```{r}
dataset %>%
  ggplot(aes(x = num_pages , y = ratings_count)) + 
  geom_col(alpha=0.7, fill = "purple") +
  labs(x = "Number of Pages", y = "Sum of Ratings") +
  ggtitle("Affection of number of pages on rating counts")
```


